Multimatrices and Their Derivatives

### 2019-07-12 Math/paper.tex
Adding proof of transpose integer isomorphism.

@@

\AtBeginEnvironment{proof}{\setcounter{ppart}{0}}
\AtBeginEnvironment{align}{\setcounter{equation}{0}}
\AtBeginEnvironment{alignat}{\setcounter{equation}{0}}

\DeclareMathOperator{\Dim}{Dim}
\DeclareMathOperator{\Ident}{I}
\DeclareMathOperator{\Tran}{Tran}
\DeclareMathOperator{\SoS}{\mathbb{S}}
\DeclareMathOperator{\Softmax}{Softmax}
\DeclareMathOperator{\Sum}{\Sigma}
%\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
%\newcommand{\mmult}[1]{\underset{#1}{\times}}
\newcommand{\mmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\times}$}}}

@@

Let's consider a traditional matrix equation. As is traditional, one matrix
$X$ shall represent the scientific education level of undergraduates, who happen
to work in a densely packed 3 by 5 grid - which is also traditional. Then let
$B$ represent the belief each of those undergradutes has in a higher power,
which, as we all know, fluctuates with respect to their scientific education in
a sinusoidal pattern (Weinersmith, 2010 \cite{weinersmith:education}).

@@

The ordering here is arbitrary, there is no reason why the dimensionality of
of the independent variable \textit{needs} to be concatenated to the right of the
dimensionality of the output. What's important is that the dimensionality of
both output and indepenedent variable are preserved. Let us declare this to
be our convention since, for the purpose of this work, mine is the divinely revealed
word of god, passed down to you lowly mortals who have yet to commit your
own mad ramblings to \LaTeX.

@@

Ok, that's neat and all but what does that actually mean? Can we answer our motivating 
question?
\[\frac{dB}{dX} = ? \]
Well... sort of. We have to abuse the notation a little and say that $B$ and $X$ are
just multimatricies with 2 dimensions. Then we can say that the total derivative
of $B$ with respect to $X$ is a multimatrix with shape $|B| \oplus |X|$,
who's elements we can define as,
\[\forall \bar{b} \in \Dim(|B|), \bar{x} \in \Dim(|X|):\]
\begin{align*}
\left( \frac{dB}{dX} \right)[\bar{b} \oplus \bar{x}]
&= \frac{\partial B[\bar{b}]}{\partial X[\bar{x}]} \\
&= \delta_{\bar{b}\bar{x}}\cos(\bar{x})
\end{align*}

@@

\begin{exercise}
Are the following assertions are true or false?
\begin{enumerate}
\item $\left<1,1,1\right> \in \Dim(\left<5,5,5\right>)$
\item $\left<1,1\right> \in \Dim(\left<5,5,5\right>)$
\item $\left<1,2,3\right> \in \Dim(\left<3,2,1\right>)$
\item $\left<3,7\right> \in \Dim(\left<3,7\right>)$
\end{enumerate}
\end{exercise}

@@

Easily done. The hard part isn't doing the calculation. The hard part is
parlaying with Sheogorath, Daedric Prince of Madness for the intellectual
property rights.

So now consider how we would multiply two matricies $A$ and $B$ if they had more
than two dimensions. Let's use a concrete example to make the problems more apparent.
Let $|A| = \left<5,7,7\right>$ and $|B| = \left<7,7,2,4\right>$.
First of all, can we even multiply the two together? Hm... maybe? $|A|$ ends with
$\left<\ldots, 7\right>$ and $|B|$ starts with $\left<7,\ldots\right>$ so it would
make sense that we can somehow squish them together into something. By that reasoning,
the shape of our after-multiplication output would use the remaining dimensions
$\left<5, 7, 7, 2, 4\right> = |A \times B|$.

@@

What we really need is an operation which covers both lines of reasoning. To do
so, we need to compleately abandon conventional algebras, and indeed any hope of
returning to sanity. That's right, we're introducing a trinary operator.

@@

\begin{theorem}[Empty Shape Multimatrix and Scalar Multiplication Equivalence]
\label{s_mm_mult_equiv}
For any multiplication operation defined between multimatricies and scalars,
the scalar may be replaced by an equivalent empty-shaped multimatrix who's
single value is that of the scalar.

@@

\begin{definition}[Multimatrix Transposition]
Let $|X| = \vec{l} \oplus \vec{r}$ where $|\vec{l}| = l$ and $|\vec{r}| = r$
\[ |\Tran(X, l)| = \vec{r} \oplus \vec{l} \]
And,
\[ \forall \bar{l} \in \Dim(\vec{l}), \bar{r} \in \Dim(\vec{r}) : \]
\[ \Tran(X, l)[\bar{r} \oplus \bar{l}] = X[\bar{l} \oplus \bar{r}] \]
\end{definition}

@@

\begin{theorem}[Inverse Transpose]
If $|X| = \vec{l} \oplus \vec{r}$
\[ \Tran(\Tran(X, |\vec{l}|), |\vec{r}|) = X \]
\end{theorem}
\begin{proof}
Let $|X| = \vec{l} \oplus \vec{r}$ then
$\forall \bar{l} \in \Dim(\vec{l}), \bar{r} \in \Dim(\vec{r}) : $
\[ \Tran(X, |\vec{l}|)[\bar{r} \oplus \bar{l}] = X[\bar{l} \oplus \bar{r}] \]
And so,
\begin{align*}
	\Tran(\Tran(X, |\vec{l}|), |\vec{r}|)[\bar{l} \oplus \bar{r}]
	&= \Tran(X, |\vec{l}|)[\bar{r} \oplus \bar{l}] \\
	&= X[\bar{l} \oplus \bar{r}] \\
\end{align*}
Therefore, 
\[ \Tran(\Tran(X, |\vec{l}|), |\vec{r}|) = X \]
\end{proof}

\begin{theorem}[Identity Transpose]
\[ \Tran(\Ident^n(\vec{x}), k|\vec{x}|) = \Ident^n(\vec{x}) \]
\end{theorem}
\begin{proof}
Consider that for some ordered set of indicies
$\{\bar{x}_1, \bar{x}_2, \ldots \bar{x}_n\} = X$ such that each
$\bar{x}_i \in X \implies \bar{x}_i \in \Dim(\vec{x})$.
Let $X'$ be some ordered permutation of $X$, then we can reason that,
\begin{align*}
 \Ident^n(\vec{x})\left[\bigoplus X'\right]
 &= 
	\left\{
  \begin{array}{ll}
    1 & \mbox{if all } \bar{x}_i \in X' \mbox{ are equal.}\\
    0 & \mbox{otherwise}
  \end{array}
	\right.\\
 &= 
	\left\{
  \begin{array}{ll}
    1 & \mbox{if all } \bar{x}_i \in X \mbox{ are equal.}\\
    0 & \mbox{otherwise}
  \end{array}
	\right.\\
 &=\Ident^n(\vec{n})\left[\bigoplus X\right]
\end{align*}
Since for
$X' = \left\{\bar{x}_{k+1}, \bar{x}_{k+2} \ldots \bar{x}_{n},
\bar{x}_1, \bar{x}_2 \ldots \bar{x}_k\right\}$
\begin{align*}
  \Tran(\Ident^n(\vec{x}), k|\vec{x}|)\left[\bigoplus X'\right]
	&=
  \Ident^n(\vec{x})\left[\bigoplus X\right]\\
	&=
  \Ident^n(\vec{x})\left[\bigoplus X'\right]
\end{align*}
Therefore
$\Tran(\Ident^n(\vec{x}), k|\vec{x}|) = \Ident^n(\vec{x})$
\end{proof}

@@

@@

\begin{theorem}[Stacked Transposition]
\[ \Tran(\Tran(A, x), y) = \Tran(A, x+y) \]
\end{theorem}
\begin{proof}
Let $|A| = \vec{x} \oplus \vec{y} \oplus \vec{a}$ where $|\vec{x}| = x$ and
$|\vec{y}| = y$. Note that,
\[ |\Tran(A, x)| = \vec{y} \oplus \vec{a} \oplus \vec{x} \]
And,
\[ |\Tran(\Tran(A, x), y)| = \vec{a} \oplus \vec{x} \oplus \vec{y} \]
Also that,
\[ |\Tran(A, x+y)| = \vec{a} \oplus \vec{x} \oplus \vec{y} \]
So $|\Tran(\Tran(A, x), y)| = \Tran(A, x+y)$ which is necessary but not
sufficient for this proof.

To show the elementwise equivalence, let $\bar{x} \in \Dim(\vec{x})$,
$\bar{y} \in \Dim(\vec{y})$, and $\bar{a} \in \Dim(\vec{a})$. Then,
\begin{align*}
  \Tran(\Tran(A, x), y)[\bar{a} \oplus \bar{x} \oplus \bar{y}]
  &= A[\bar{x} \oplus \bar{y} \oplus \bar{a}] \\
  &= \Tran(A, x+y)[\bar{a} \oplus \bar{x} \oplus \bar{y}]
\end{align*}
Which shows that $\Tran(\Tran(A, x), y) = \Tran(A, x+y)$
\end{proof}

@@

@@

\begin{displayquote}
``I'm not saying Machine Learning is a portal to a demon universe, I'm just saying
that some doors are best left unopened.'' - James Mickens, AKA `Galactic Viceroy of Research Excellence', USENIX Security '18-Q
\end{displayquote}

@@

\begin{theorem}[Derivative of Sum of Squares]
\[ \frac{d \SoS(X)}{dX} = 2X \]
\end{theorem}
\begin{proof}
Notice that $\SoS(X) = X \mmult{|\vec{x}|} X$...

TODO
\end{proof}

>>>>

\newtheoremstyle{case}{}{}{}{}{}{:}{ }{}
\theoremstyle{case}
\newtheorem{case}{Case}

@@

\AtBeginEnvironment{proof}{\setcounter{ppart}{0}}
\AtBeginEnvironment{proof}{\setcounter{case}{0}}
\AtBeginEnvironment{align}{\setcounter{equation}{0}}
\AtBeginEnvironment{alignat}{\setcounter{equation}{0}}

\DeclareMathOperator{\Dim}{Dim}
\DeclareMathOperator{\Ident}{I}
\DeclareMathOperator{\Tran}{Tran}
\DeclareMathOperator{\SoS}{\mathbb{S}}
\DeclareMathOperator{\Softmax}{Softmax}
\DeclareMathOperator{\Sum}{\Sigma}
\DeclareMathOperator{\remainder}{mod}
%\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
%\newcommand{\mmult}[1]{\underset{#1}{\times}}
\newcommand{\mmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\times}$}}}

@@

Let us consider a traditional matrix equation - one contrived on the spot for the
purposes of adding an additional layer of confusion to the situation.

As is tradition, let one matrix $X$ represent the scientific education level of
undergraduates, who work in a densely packed 3 by 5 grid (which is also traditional).
Then let $B$ represent the belief each of those undergradutes has in a higher power.

It has been shown that an undergraduate's belief in a higher power fluctuates with
respect to their scientific education in a sinusoidal pattern
(Weinersmith, 2010 \cite{weinersmith:education}).

@@

The ordering here is arbitrary. There is no reason why the dimensionality of
of the independent variable \textit{needs} to be concatenated to the right of the
dimensionality of the output. What's important is that the dimensionality of
both output and indepenedent variable are preserved. Let us declare this to
be our convention since, for the purpose of this work, mine is the divinely revealed
word of god, graciously passed down to you lowly mortals (I've typeset
my mad ranblings with \LaTeX ~therefore they must be reasonably coherent. QED).

@@

Ok, that's neat and all but what does that actually mean? Can we answer our motivating 
question?
\[\frac{dB}{dX} = ? \]
Well... sort of. We have to abuse the notation a little and say that $B$ and $X$ are
just multimatricies with 2 dimensions. Then we can say that the total derivative
of $B$ with respect to $X$ is a multimatrix with shape $|B| \oplus |X|$,
whose elements we can define as,
\[\forall \bar{b} \in \Dim(|B|), \bar{x} \in \Dim(|X|):\]
\begin{align*}
\left( \frac{dB}{dX} \right)[\bar{b} \oplus \bar{x}]
&= \frac{\partial B[\bar{b}]}{\partial X[\bar{x}]} \\
&= \delta_{\bar{b}\bar{x}}\cos(\bar{x})
\end{align*}

@@

\begin{exercise}
True or false?
\begin{enumerate}
\item $\left<1,1,1\right> \in \Dim(\left<5,5,5\right>)$
\item $\left<1,1\right> \in \Dim(\left<5,5,5\right>)$
\item $\left<1,2,3\right> \in \Dim(\left<3,2,1\right>)$
\item $\left<3,7\right> \in \Dim(\left<3,7\right>)$
\end{enumerate}
\end{exercise}

@@

Easily done. The hard part isn't doing the calculation. The hard part getting over
your naive belief that mathematical operations should be rooted in some concrete
concept rather than ``this is the way it's done because it makes the equations
you'll see later work.''

So now consider how we would multiply two matricies $A$ and $B$ if they had more
than two dimensions. Let's use a concrete example to make the problems more
structurally sound.
Let $|A| = \left<5,7,7\right>$ and $|B| = \left<7,7,2,4\right>$.
First of all, can we even multiply the two together? Hm... maybe? $|A|$ ends with
$\left<\ldots, 7\right>$ and $|B|$ starts with $\left<7,\ldots\right>$ so it would
make sense that we can somehow squish them together into something. By that reasoning,
the shape of our after-multiplication output would use the remaining dimensions
$\left<5, 7, 7, 2, 4\right> = |A \times B|$.

@@

What we really need is an operation which covers both lines of reasoning. To do
so, we need to compleately abandon conventional algebras, and indeed any hope of
returning to sanity. That's right, we're introducing a ternary operator.

@@

\begin{theorem}[Empty Shape Multimatrix and Scalar Multiplication Equivalence]
\label{s_mm_mult_equiv}
For any multiplication operation defined between multimatricies and scalars,
the scalar may be replaced by an equivalent empty-shaped multimatrix whose
single value is that of the scalar.

@@

\begin{definition}[Multimatrix Transposition]
\label{tran_def}
Let $|X| = \vec{l} \oplus \vec{r}$ where $|\vec{l}| = l$ and $|\vec{r}| = r$
\[ |\Tran(X, l)| = \vec{r} \oplus \vec{l} \]
And,
\[ \forall \bar{l} \in \Dim(\vec{l}), \bar{r} \in \Dim(\vec{r}) : \]
\[ \Tran(X, l)[\bar{r} \oplus \bar{l}] = X[\bar{l} \oplus \bar{r}] \]
We call $l$ the index of transpose.
\end{definition}

@@

However, you'll see cases in later chapters of multimatrix transposes where
the index of transpose is larger than the size of the shape matrix. So we need
to make sense of that operation as well. Fortunately, there is a logical way
to extend the definition. Consider that this transposition can be reasonably
shown to be equivalent to moving the first index of the shape matrix
to the end of the shape matrix over and over again, this can be done any number
of times, therefore doing so for more than the size of the shape matrix still works,
it just requires a bit of modular arithmetic.

\begin{definition}[Multimatrix Transpose Extension]
\label{tran_ext}
For any multimatrix, the following transposes are equivalent,
\[ \Tran(X, n) = \Tran(X, \remainder(n, ||X||)) \]
Where $\remainder(n, ||X||)$ is the remainder of $n$ divided by $||X||$.
That is, a value $0 \le \remainder(n, ||X||) < ||X||$ such that there exists an
integer $k$ where, $n = k||X|| + \remainder(n, ||X||)$.
\end{definition}

This extension is consisent with the prevous definition because, for any
index of transpose, $l$, that would be covered by the original definition,
$0 \le l \le ||X||$, you can see that, in all but one case $\remainder(l, ||X||) = l$.
The exception, $l = ||X||$ is covered by showing that
$\remainder(||X||, ||X||) = 0$ and $\Tran(X, 0) = \Tran(X, ||X||)$.

Thus, we (by which I mean \textit{me} since \textit{you} certainly haven't done any
of the work) have shown a natural equivalent class \cite{book:abstract} of transpose
operations. On multimatricies with a shape of some length $n$ there are $n$ unique
transpose; $\Tran(X, i)$ for all $0 \le i < n$. All other transposes are equivalent
to one of these base transposes by our extended definition.

To make use of this equivalence, we need to first show how these classes are
isomorphic \cite{book:abstract} to a more manageable group.

\begin{theorem}[Isomorphism of Transpostion and Modular Integers]
\label{tran_int_iso}
Let $\mathbb{T}_n$ be the set of possible transpositions on multimatricies with
shapes of length $n$. Let $\circ$ be the operation of composition. Then
$(\mathbb{T}_n, \circ)$ is a group which is isomorphic to the group of
integers mod $n$ under addition. That is,
\[ (\mathbb{T}_n, \circ) \cong (\mathbb{Z}_n, +) \]
\end{theorem}
\begin{proof}
I'll need to tackle this proof in two parts. First I'll need to show that
that set of transpositions is a group under composition, then I'll need to
provide a one-to-one and onto map that preseves the respective group operations
between transpositions and integers mod $n$.

\begin{ppart}
To begin, I'll show that the set of all transpositions on multimatricies 
with shapes of length $n$ form a group under composition.

Let's look at the composition of some two transposes on a multimatrix.
So, let $A$ be a multimatrix with shape of length $n$. Now let $x$ and $y$
be indicies of transpositions. Then what is $\Tran(\Tran(A, x), y)$?
To apply the the first transpose we need to break $|A|$ into two vectors,
so let $|A| = \vec{l} \oplus \vec{r}$ where $|\vec{l}| = x$.

Then,
\[ |\Tran(A, x)| = \vec{r} \oplus \vec{l} \]
And for all
$\bar{l} \in \Dim(\vec{l})$ and $\bar{r} \in \Dim(\vec{r})$,
\[ \Tran(A, x)[\bar{r} \oplus \bar{l}] = A[\bar{l} \oplus \bar{r}] \]

Now to apply a transposition with index of transposition $y$ to $\Tran(A,x)$
we need to break up $|\Tran(A,x)|$ into two vector, such as
$|\Tran(A,x)| = \vec{l}' \oplus \vec{r}'$.

Since we've already shown that $|\Tran(A,x)| = \vec{r} \oplus \vec{l}$
we end up with two conceptual splits of that shape vector that need to
be reconciled.

\begin{case} $|\vec{l}'| \le |\vec{r}|$

Then we can divide $|\Tran(A,x)|$ into three vectors, $\vec{a}$, $\vec{b}$, and $\vec{c}$
such that
\[ |\Tran(A,x)| = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
\[ \vec{l}' = \vec{b} \]
\[ \vec{r}' = \vec{c} \oplus \vec{a} \]
\[ \vec{r} = \vec{b} \oplus \vec{c} \]
\[ \vec{l} = \vec{a} \]
It helps to think of the $\oplus$ operation as a cut in two separate places in the same
vector because of the two conceptual splits from the two transpositions to see why this
logic is valid.

So we can then say,
\[ |A| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]

And since,
\[ |\Tran(\Tran(A, x), y)| = \vec{r}' \oplus \vec{l}' \]
It follows that,
\[ |\Tran(\Tran(A, x), y)| = \vec{c} \oplus \vec{a} \oplus \vec{b} \]

Now, let $\bar{a} \in \Dim(\vec{a})$, $\bar{b} \in \Dim(\vec{b})$, and
$\bar{c} \in \Dim(\vec{c})$. Notice that because of Theorem 
\ref{dim_set_ind_concat_thm}, $\bar{c} \oplus \bar{a} \in \Dim(\vec{r}')$ and
$\bar{b} \oplus \bar{c} \in \Dim(\vec{r})$.

Continuing our definition of transposition,
\begin{align*}
  \Tran(\Tran(A, x), y)[\bar{c} \oplus \bar{a} \oplus \bar{b}]
  &=
  \Tran(A, x)[\bar{b} \oplus \bar{c} \oplus \bar{a}] \\
  &=
  A[\bar{a} \oplus \bar{b} \oplus \bar{c}]
\end{align*}

See now that this composit operation is also a transposition, $\Tran(A, z)$ where,
$z = |\vec{a} \oplus \vec{b}|$.
So by definition,
\begin{align*}
  |\Tran(A, z)|
  &=
  \vec{c} \oplus \vec{b} \oplus \vec{a} \\
  &=
  |\Tran(\Tran(A, x), y)|  
\end{align*}
And,
\begin{align*}
  \Tran(A, z)[\bar{c} \oplus \bar{a} \oplus \bar{b}]
  &=
  A[\bar{a} \oplus \bar{b} \oplus \bar{c}] \\
  &=
  \Tran(\Tran(A, x), y)[\bar{c} \oplus \bar{a} \oplus \bar{b}]
\end{align*}
\end{case}

\begin{case} $|\vec{l}'| > |\vec{r}|$
Then we can divide $|\Tran(A,x)|$ into three vectors, $\vec{a}$, $\vec{b}$, and $\vec{c}$
such that
\[ |\Tran(A,x)| = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
\[ \vec{l}' = \vec{c} \oplus \vec{a} \]
\[ \vec{r}' = \vec{b} \]
\[ \vec{r} = \vec{c} \]
\[ \vec{l} = \vec{a} \oplus \vec{b} \]

So we can then say,
\[ |A| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]

And since,
\[ |\Tran(\Tran(A, x), y)| = \vec{r}' \oplus \vec{l}' \]
It follows that,
\[ |\Tran(\Tran(A, x), y)| = \vec{b} \oplus \vec{c} \oplus \vec{a} \]

Now, let $\bar{a} \in \Dim(\vec{a})$, $\bar{b} \in \Dim(\vec{b})$, and
$\bar{c} \in \Dim(\vec{c})$. Notice that because of Theorem 
\ref{dim_set_ind_concat_thm}, $\bar{c} \oplus \bar{a} \in \Dim(\vec{l}')$ and
$\bar{a} \oplus \bar{b} \in \Dim(\vec{l})$.

Continuing our definition of transposition,
\begin{align*}
  \Tran(\Tran(A, x), y)[\bar{b} \oplus \bar{c} \oplus \bar{a}]
  &=
  \Tran(A, x)[\bar{c} \oplus \bar{a} \oplus \bar{b}] \\
  &=
  A[\bar{a} \oplus \bar{b} \oplus \bar{c}]
\end{align*}

See now that this composit operation is also a transposition, $\Tran(A, z)$ where,
$z = |\vec{a}|$.
So by definition,
\begin{align*}
  |\Tran(A, z)|
  &=
  \vec{b} \oplus \vec{c} \oplus \vec{a} \\
  &=
  |\Tran(\Tran(A, x), y)|  
\end{align*}
And,
\begin{align*}
  \Tran(A, z)[\bar{b} \oplus \bar{c} \oplus \bar{a}]
  &=
  A[\bar{a} \oplus \bar{b} \oplus \bar{c}] \\
  &=
  \Tran(\Tran(A, x), y)[\bar{b} \oplus \bar{c} \oplus \bar{a}]
\end{align*}
\end{case}

So I've shown that in both cases, the composit function of two transposes is
itself a transpose. So transposes of multimatrcies of shape of length $n$ are
a closed group under composition. Of.
\end{ppart}

\begin{ppart}
In this last part, I'll define a bijective map
$\phi: \mathbb{T}_n \to \mathbb{Z}_n$ for which
\[ \phi(\Tran_y \circ \Tran_x) = \phi(\Tran(y)) + \phi(\Tran(x)) \]
Which is the definition of an isomorphism.

Note that I'm letting $\Tran_i$ be a shorthand for ``a transposition
with index of transposition $i$ that is in $\mathbb{T}_n$''.

So let's just define $\phi$.
\[ \phi(\Tran_i) = i \]
Done. I'm a genious.

Ok, the hard part is showing that it preserves the group operations.
Let's go back to our example in the first part of this proof. Let $A$ be
any multimatrix with shape length $n$. Then let there be two transpositons
$\Tran_x$ and $\Tran_y$ which we'll apply in series. First remember that
to define $\Tran_x$ we needed to divide $|A|$ into $|A| = \vec{l} \oplus \vec{r}$
where $|\vec{l}| = x$. Then we'd say that
\[ |\Tran(A, x)| = \vec{r} \oplus \vec{l} \]
Then to further apply $\Tran(\Tran(A, x), y)$ we need to divide $|\Tran(A,x)|$
into,
\[ |\Tran(A, x)| = \vec{l}' \oplus \vec{r}' \]
Where $|\vec{l}'| = y$.
That leads to two cases,

\setcounter{case}{0}
\begin{case} $|\vec{l}'| \le |\vec{r}|$

And in this case we showed that we needed to split up $|A|$ into,
\[ |A| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
\[ \vec{l}' = \vec{b} \]
\[ \vec{r}' = \vec{c} \oplus \vec{a} \]
\[ \vec{r} = \vec{b} \oplus \vec{c} \]
\[ \vec{l} = \vec{a} \]

So that,
\[ |\Tran(A, x)| = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
\[ |\Tran(\Tran(A, x), y)| = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
And note that,
\[ x = |\vec{a}| \]
\[ y = |\vec{b}| \]

And we showed that the composit $\Tran_z = \Tran_y \circ \Tran_x$ was such
that,
\[ z = |\vec{a} \oplus \vec{b}| \]

Consider that $\phi(\Tran_z) = z$, and so,
\begin{align*}
  z
  &= |\vec{a} \oplus \vec{b}| \\
  &= |\vec{a}| + |\vec{b}| \\
  &= x + y \\
  &= y + x \\
  z &\equiv y + x \mod n \\
  \phi(\Tran_z) &= \phi(\Tran_y) + \phi(\Tran_x) \\
  \phi(\Tran_y \circ \Tran_x) &= \phi(\Tran_y) + \phi(\Tran_x)
\end{align*}
So in this case the isomorphism works.
\end{case}

\begin{case} $|\vec{l}'| > |\vec{r}|$

And in this case we showed that we needed to split up $|A|$ into,
\[ |A| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
\[ \vec{l}' = \vec{c} \oplus \vec{a} \]
\[ \vec{r}' = \vec{b} \]
\[ \vec{r} = \vec{c} \]
\[ \vec{l} = \vec{a} \oplus \vec{b} \]

So that,
\[ |\Tran(A, x)| = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
\[ |\Tran(\Tran(A, x), y)| = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
And note that,
\[ x = |\vec{a} \oplus \vec{b}| \]
\[ y = |\vec{c} \oplus \vec{a}| \]

And we showed that the composit $\Tran_z = \Tran_y \circ \Tran_x$ was such
that,
\[ z = |\vec{a}| \]

Consider that $\phi(\Tran_z) = z$, and so,
\begin{align*}
  z
  &= |\vec{a}| \\
  &\equiv |\vec{a}| + n \mod n \\
  &\equiv |\vec{a}| + |\vec{a} \oplus \vec{b} \oplus \vec{c}| \mod n \\
  &\equiv |\vec{a} \oplus \vec{a} \oplus \vec{b} \oplus \vec{c}| \mod n \\
  &\equiv |\vec{c} \oplus \vec{a} \oplus \vec{a} \oplus \vec{b}| \mod n \\
  &\equiv |\vec{c} \oplus \vec{a}| + |\vec{a} \oplus \vec{b}| \mod n \\
  &\equiv y + x \mod n \\
  \phi(\Tran_z) &= \phi(\Tran_y) + \phi(\Tran_x) \\
  \phi(\Tran_y \circ \Tran_x) &= \phi(\Tran_y) + \phi(\Tran_x)
\end{align*}
So also in this case the isomorphism works.
\end{case}

So, in both cases $\phi$ is a valid isomorphism between $(\mathbb{T}_n, \circ)$
and $(\mathbb{Z}_n, +)$.
\end{ppart}
\end{proof}

Well what does that mean? I'm so glad you asked... weirdo who doesn't know what
an isomorphism is but is several chapters into a hobby math book. It means that...

\begin{corollary}[Stacked Transpose]
For any multimatrix $A$ whose shape is $n$ long (an $n$ dimensional multimatrix
in other words), it is always true that
\[ \Tran(\Tran(A, x),y) = \Tran(A, \remainder(x+y,n)) \]
\end{corollary}

\begin{example}
Let's take a look at a concrete example. Say we have a
multimatrix $A$ who's shape is $\left<11, 3, 7, 5\right>$. 
Then see that,
\[ |\Tran(A, 2)| = \left<7, 5, 11, 3\right> \]
And applying another transpose,
\[ |\Tran(\Tran(A, 2), 3)| = \left<3, 7, 5, 11\right> \]
Notice that our corollary says that this double transpose should be
equal to the transpose $\Tran(A, \remainder(2+3, 4))$ which would
be $\Tran(A, 1)$ and indeed it is:
\begin{align*}
  |\Tran(A, 1)|
  &= \left<3, 7, 5, 11\right> \\
  &= |\Tran(\Tran(A, 2), 3)|
\end{align*}
\end{example}

Another useful corollary from Theorem \ref{tran_int_iso} shows you how to
undo transposition operations with other transposition operations.

\begin{corollary}[Inverse Transpose]
Let $A$ be a multimatrix such that $||A|| = n$. And let
$x$ be some integer. Then, the inverse of $\Tran_x$ is
$\Tran_{-x}$. That is,
\[ \Tran(\Tran(A, x), -x) = X \]
\end{corollary}

\begin{example}
Say you have a multimatrix, $A$, of shape $\left<2,7,1,8,3\right>$.
Let's apply a transpose to it, $\Tran_3$, and we'll get the shape,
\[ |\Tran(A, 3)| = \left<8,3,2,7,1\right> \]
Now, to get back to $A$ we can apply another transpose $\Tran_{-3}$ according
to the above corollary.
Our extended definition of transposition (Def. \ref{tran_ext})
tells us that this is equal to $\Tran_{\remainder(-3, 5)} = \Tran_{2}$.
So the inverse of $\Tran_3$ is $\Tran_2$, which we can see here:
\begin{align*}
  |\Tran(\Tran(A, 3), 2)|
  &= \left<2,7,1,8,3\right> \\
  &= |A|
\end{align*}
\end{example}

TODO: explosition

\begin{theorem}[Identity Transpose]
TODO: setup
\[ \Tran(\Ident^n(\vec{x}), k|\vec{x}|) = \Ident^n(\vec{x}) \]
\end{theorem}
\begin{proof}
Consider that for some ordered set of indicies
$\{\bar{x}_1, \bar{x}_2, \ldots \bar{x}_n\} = X$ such that each
$\bar{x}_i \in X \implies \bar{x}_i \in \Dim(\vec{x})$.
Let $X'$ be some ordered permutation of $X$, then we can reason that,
\begin{align*}
 \Ident^n(\vec{x})\left[\bigoplus X'\right]
 &= 
	\left\{
  \begin{array}{ll}
    1 & \mbox{if all } \bar{x}_i \in X' \mbox{ are equal.}\\
    0 & \mbox{otherwise}
  \end{array}
	\right.\\
 &= 
	\left\{
  \begin{array}{ll}
    1 & \mbox{if all } \bar{x}_i \in X \mbox{ are equal.}\\
    0 & \mbox{otherwise}
  \end{array}
	\right.\\
 &=\Ident^n(\vec{n})\left[\bigoplus X\right]
\end{align*}
Since for
$X' = \left\{\bar{x}_{k+1}, \bar{x}_{k+2} \ldots \bar{x}_{n},
\bar{x}_1, \bar{x}_2 \ldots \bar{x}_k\right\}$
\begin{align*}
  \Tran(\Ident^n(\vec{x}), k|\vec{x}|)\left[\bigoplus X'\right]
	&=
  \Ident^n(\vec{x})\left[\bigoplus X\right]\\
	&=
  \Ident^n(\vec{x})\left[\bigoplus X'\right]
\end{align*}
Therefore
$\Tran(\Ident^n(\vec{x}), k|\vec{x}|) = \Ident^n(\vec{x})$
\end{proof}

TODO: exposition here

@@

TODO: exposition here

@@

@@

\label{multiplication_rule}

@@

\begin{displayquote}
``I'm not saying Machine Learning is a portal to a demon universe, I'm just saying
that some doors are best left unopened.'' - James Mickens, AKA `Galactic Viceroy of Research Excellence', USENIX Security 2018
\end{displayquote}

@@

\begin{theorem}[Derivative of Sum of Squares]
Let $X$ be any multimatrix then,
\[ \frac{d \SoS(X)}{dX} = 2X \]
\end{theorem}
\begin{proof}
Let $|X| = \vec{x}$. Notice that $\SoS(X) = X \mmult{|\vec{x}|} X$ since,
$|X \mmult{|\vec{x}|} X| = \left<\right>$ and,
\[
  \left(X \mmult{|\vec{x}|} X\right)[\left<\right> \oplus \left<\right>]
  =
  \sum_{\forall \bar{x} \in \Dim(\vec{x})}
    X[\left<\right> \oplus \bar{x}]
    X[\bar{x} \oplus \left<\right>]
\]
Then, by the multiplication rule (Thm. \ref{multiplication_rule}),
\begin{align*}
  \frac{d\left(X \mmult{|\vec{x}|} X\right)}{dX}
  &=
  X \mmult{|\vec{x}|} \frac{dX}{dX} +
  \Tran\left(
    \Tran(X, |\vec{x}|)
      \mmult{|\vec{x}|}
    \Tran\left(\frac{dX}{dX}, |\vec{x}|\right),
    |\vec{x} \oplus \vec{x}|
  \right) \\
  &=
  X \mmult{|\vec{x}|} \Ident^2(|X|) +
  \Tran\left(
    X
      \mmult{|\vec{x}|}
    \Tran\left(\Ident^2(|X|), |\vec{x}|\right),
    |\vec{x} \oplus \vec{x}|
  \right) \\
  &=
  X +
  \Tran\left(
    X
      \mmult{|\vec{x}|}
    \Ident^2(|X|),
    |\vec{x} \oplus \vec{x}|
  \right) \\
  &=
  X +
  \Tran\left(
    X,
    |\vec{x} \oplus \vec{x}|
  \right) \\
  &= X + X \\
  &= 2X
\end{align*}
\end{proof}
